\begin{thebibliography}{99}

\bibitem{Apo}
  Apostolico A., Galil Z.,
  \textit{Pattern matching algorithms},
  Oxford University Press,
  1997
  
\bibitem{Bil}
  Bille P,
  \textit{A survey on tree edit distance and related problems},
  Theoretical computer science,
  2005,
  217–-239
  
\bibitem{Boe}
  Böcker S., Canzar S., Klau G.,
  \textit{The Generalized Robinson-Foulds Metric},
  International Workshop on Algorithms in Bioinformatics,
  2013,
  156–-169,
  
\bibitem{Bog}
  Bogdanowicz D., Giaro K. and Wróbel B.,
  \textit{TreeCmp: Comparison of Trees in Polynomial Time},
  Evolutionary Bioinformatics 8,
  2012,
  475--487
   
\bibitem{Che}
  Chen W.
  \textit{New algorithm for ordered tree-to-tree correction problem},
  J. Algor. 40,
  2001,
  135--158
  
\bibitem{Dem}
  Demaine E. D., Mozes S., Rossmann B. and Weimann O.,
  \textit{An Optimal Decomposition Algorithm for Tree Edit Distance},
  ICALP'07 Proceedings of the 34th international conference on Automata, Languages and Programming,
  2007,
  146--157

\bibitem{DulAndTou}
  Dulucq S. and Touzet H.,
  \textit{Analysis of tree edit distance algorithms},
  Proceedings of the 14th Annual Symposium on Combinatorial Pattern Matching (CPM),
  2003,
  83--95
  
\bibitem{Git}
  Andritsch C.,
  \textit{Master Thesis},
  Github Repository,
  \url{https://github.com/bananajoe/masters_thesis},
  2019
  
\bibitem{Har}
  Harel D. and Tarjan R. E.,
  \textit{Fast algorithms for finding nearest common ancestors},
  SIAM J. Comput. 13, 2,
  1984,
  338--355
  
\bibitem{Hen}
  Tim Henderson
  \textit{Zhang-Shasha: Tree edit distance in Python},
  Github Repository,
  \url{https://github.com/timtadh/zhang-shasha},
  2019
  
\bibitem{Kle}
  Klein P. N.,
  \textit{Computing the edit-distance between unrooted trees}, 
  Proceedings of the 6th Annual European Symosium on Algorithms (ESA),
  1998,
  91--102
  
\bibitem{Kum}
  Kumar R., Talton J., Ahmad S., Roughgarden T., Klemmer S.,
  \textit{Flexible Tree Matching},
  Proceedings of the 22nd International Joint Conference on Artificial Intelligence,
  2011,
  
\bibitem{Moo}
  Moore P.,
  \textit{Strucural motifs in RNA},
  Ann. Rev. Biochem 68,
  1999,
  287--300
  
\bibitem{SasAndZha}
  Sasha D. and Zhang K.,
  \textit{Simple fast for editin distance between trees and related problems},
  SIAM J. Comput. 18, 6,
  1989,
  1245--1262
  
\bibitem{Tai}
  Tai K.,
  \textit{The tree-to-tree correction problem},
  J. Assoc. Comp. Mach. 26,
  1979,
  422--433
  
\bibitem{Val}
  Valiente G.,
  \textit{Algorithms on Trees and Graphs},
  Springer-Verlag,
  2002,
  
\bibitem{Wag}
  Wagner R. and Fischer M. J.,
  \textit{The string-to-string correction problem},
  J. ACM 21, 1,
  1974,
  168--173
  
\end{thebibliography}